### 2025-05-06 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update msuRACiFit_rice_params.Rmd

#ABSOLUTE PATHS
A330502WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
A330502WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
A330504WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
A330504WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
A330506WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
A330506WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
A330509WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
A330509WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")

>>>>

#ABSOLUTE PATHS
A330502WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
A330502WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
A330504WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
A330504WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
A330506WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
A330506WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
A330509WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
A330509WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")
